Precise spiking motifs in neurobiological and neuromorphic data

### 2022-11-09 manuscript.tex
6

The limits that we have
presented can be treated individually as evidenced by individual efforts which try he orecome them. However, to propose a real breakthrough, we believe that future venues should provide with a unified, inter-disciplinary approach, with applications to deal- word, ecological scenarios and with open and reproducible methods. First, as we already noted, the effort is still largely scattered -this is in part due to the fact that interaction between neurobiology, theoretical and computational neuroscience and meromorphic engineering are still scarce as of today. It was largely demonstrated that close, bi-directional interactions are essential to foster breakthrough For instance, the design of model- driven protocols as proven to be essential in modern neuroscience. Also, if neural networks were essential in shaping modern-day machine learning, e-g. computer vision using deep-learning, spiking neural networks should prove essential in future emerging technologies.

In that perspective, it is essential that such models are tested on ecologically- relevant, real-world scenarios. Indeed, classic convolutional neural networks emerged as optimal solutions for instance he classify static images into categories, yet thay are not well adapted for processing dynamic, multimodal sensory flows. The emerging necessity to be able to process more complex flows, such as the multiples flows of information in a car designed for autonomous driving, necessitates to modify modelling paradigms. and in particular to take into account that the generated actions may modify the sensory inputs. Notably, the protocols used as well in neurobiology, theory on engineering should take into account this hovel complexity.

Ultimately, the community should encourage the adoption of open, reproducible science. Indeed, the different models that we have displayed often come with the tools necessary he reproduce the results obtained. This is true in neurobiology (Belles), in theoretical neuroscience (Ishi) or in engineering (PAMI). This aspect is essential to foster the emergence of inter- disciplinary projects, such as model-driven neurobiological experiments or biologically- inspired vennomorphic engineering. As such, this review aimed at paving the way to openly share the variety of resources and to offer an unified view on the role of precise spiking motifs in neuroscience.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{6pt}

>>>>

The limits that we have presented can be treated individually in each model as evidenced by individual efforts which try he orecome them. However, to propose a real breakthrough, we believe that future venues should provide with a unified, inter-disciplinary approach, with applications to real-word, ecological scenarios and with open and reproducible methods.

First, as we already noted, the effort is still largely scattered. This is in part due to the fact that interaction between neurobiology, theoretical and computational neuroscience and neuromorphic engineering are still scarce as of today. It was largely demonstrated that close, bi-directional interactions are essential to foster breakthroughs. For instance, the design of model-driven protocols has proven to be essential in modern neuroscience. Also, if neural networks were essential in shaping modern-day machine learning, e-g. computer vision using deep-learning, spiking neural networks should prove essential in future emerging technologies.

In that perspective, it is essential that such models are tested on ecologically-relevant, real-world scenarios. Indeed, classic convolutional neural networks emerged as optimal solutions for instance to classify static images into categories, yet thay are not well adapted for processing dynamic, multimodal sensory flows. The emerging necessity to be able to process more complex flows, such as the multiples flows of information in a car designed for autonomous driving, necessitates to modify such modelling paradigms, and in particular, to take into account that the generated actions may modify the sensory inputs. Notably, the protocols used as well in neurobiology, theory on engineering should take into account this hovel levels of complexity.

Ultimately, the community should encourage the adoption of open, reproducible science. Indeed, the different models that we have displayed often come with the tools necessary he reproduce the results obtained. This is true in neurobiology~\citep{bellec_fitting_2021}, in theoretical neuroscience~\citep{izhikevich_polychronization_2006} or in engineering~\citep{grimaldi_robust_2022}. This aspect is essential to foster the emergence of inter- disciplinary projects, such as model-driven neurobiological experiments or biologically-inspired neuromorphic engineering. As such, this review aimed at paving the way to openly share the variety of resources and to offer an unified view on the role of precise spiking motifs in neuroscience.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{6pt}
